Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-08-29 paper.tex
fixing some typos

As far as the different methods are concerned, M5P model obtained the best results, both in time and error. The advantage of M5P is that it can learn and tackle classification tasks that have high dimensionality and categorical variables efficiently. Moreover, M5P generates reproducible and comprehensible representations that provide information on the decision process and does not require human intervention either for the operation or for interpretation. Thus, it is very suitable model be incorporated in a publishing company 
processes (as we will show in Section \ref{subsec:decision_trees}).

@@

According to Table \ref{tab:all_publishers_no_fs}, it can also be noticed that the Linear Regression model outperforms some other complex methods like the Random Forest, both in time and in obtained errors. Although, Linear regression is considered as a simple model to build, more powerful models can obtain better results in comparable time.

@@

After applying the feature selection process, we have run the same
forecasting models as in Section \ref{subsec:results_all_publishers}
for the whole dataset (all the publishers), but considering only the
selected features by each method. The results are shown in Table
\ref{tab:results_all_publishers_fs}. Examining the obtained results
for each feature selection method, it can be seen that RFE got the
best results compared to SOM and CSE. It can be noticed also that we
obtain better performance in M5P, kNN and RF using only features
selected by RFE than using all features. %Better publish results in
                                %the same table or refer to the table
                                %where it was published. Is this
                                %difference statistically significant?
                                %- JJ
As expected, in general, all feature selection methods have reduced the training time needed to build the forecasting methods. This is because they reduced the considered features and mainly because they excluded the categorical features, which are the hardest to be managed (they have many possible values). On the other side, CSE and SOM did not perform as good as RA. This could be explained due to the extensive reduction made by CSE and due to the `subjective' (but not so accurate) human intervention in the case of SOM.

>>>>

As far as the different methods are concerned, M5P model obtained the best results, both in time and error. The advantage of M5P is that it can learn and tackle classification tasks that have high dimensionality and categorical variables efficiently. Moreover, M5P generates reproducible and comprehensible representations that provide information on the decision process and does not require human intervention either for the operation or for interpretation. Thus, it is a very suitable model be incorporated in a publishing company 
processes (as we will show in Section \ref{subsec:decision_trees}).

@@

According to Table \ref{tab:all_publishers_no_fs}, it can also be noticed that 
the Linear Regression model outperforms some other complex methods like the 
Random Forest, both in time and in obtained errors. 
Although, Linear Regression is considered as a simple model to build, more 
powerful models can obtain better results in comparable time.

@@

After applying the feature selection process, we have run the same
forecasting models as in Section \ref{subsec:results_all_publishers}
for the whole dataset (all the publishers), but considering only the
selected features by each method. The results are shown in Table
\ref{tab:results_all_publishers_fs}. Examining the obtained results
for each feature selection method, it can be seen that RFE got the
best results compared to SOM and CSE. It can be noticed also that we
obtain better performance using M5P, kNN and RF with the set of features
selected by RFE than using all features. %Better publish results in
                                %the same table or refer to the table
                                %where it was published. Is this
                                %difference statistically significant?
                                %- JJ
As expected, in general, all feature selection methods have reduced the training time needed to build the forecasting methods. This is because they reduced the considered features and mainly because they excluded the categorical features, which are the hardest to be managed (they have many possible values). On the other side, CSE and SOM did not perform as good as RA. This could be explained due to the extensive reduction made by CSE and due to the `subjective' (but not so accurate) human intervention in the case of SOM.
